Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
fix borger

<!-- mov -->
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Collective movement can reduce per capita predation
risk via detection-dilution trade-offs and improve information transfer about
the quality or location of resources [@Jolles_2019]. Multilayer networks could
be constructed from layers defined by movement parameters, given the existing
framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
edges could represent measures of collective movement based on dynamic
interaction metrics [@Long_2014]. We generated multilayer networks based on
habitat-specific layers of social association. Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. For
example, social processes may be an emergent property of the landscape because
animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
Movement to, from, or within habitat patches or territories can also contribute
to the formation of the social environment [@Spiegel_2016]. For example, in
sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology <!-- TODO: fix-->[@Border_2020] have enabled this
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
<!-- mov -->

>>>>

<!-- mov -->
Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Collective movement can reduce per capita predation
risk via detection-dilution trade-offs and improve information transfer about
the quality or location of resources [@Jolles_2019]. Multilayer networks could
be constructed from layers defined by movement parameters, given the existing
framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
edges could represent measures of collective movement based on dynamic
interaction metrics [@Long_2014]. We generated multilayer networks based on
habitat-specific layers of social association. Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. For
example, social processes may be an emergent property of the landscape because
animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
Movement to, from, or within habitat patches or territories can also contribute
to the formation of the social environment [@Spiegel_2016]. For example, in
sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology <!-- TODO: fix-->[@Borger_2020] have enabled this
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
<!-- mov -->
